Placeholder for article 3

### 2025-01-13 analysis/paper/paper.qmd
Tool-to-debitage ratio graph

>>>>

```{r}
#| label: fig-ratiotd
#| fig-cap: Plotted ratios of tools-to-debitage by chert types (x axis) and assemblage (colour). Distance to source groups (local and non-local) are marked by different shapes.

gravettian_ratiotd_b <-gravettian_ratiotd %>% 
  dplyr::mutate("Assemblage" = "Gravettian") %>% 
  select(Assemblage, RMTYPE, `Tool/Blank`)
proto_ratiotd_b <- proto_ratiotd %>% 
  dplyr::mutate("Assemblage" = "Proto-Solutrean") %>% 
  select(Assemblage, RMTYPE, `Tool/Blank`)
solutrean_ratiotd_b <- solutrean_ratiotd %>% 
  dplyr::mutate("Assemblage" = "Solutrean") %>% 
  select(Assemblage, RMTYPE, `Tool/Blank`)
ratio_tooldebitage <- bind_rows(gravettian_ratiotd_b, proto_ratiotd_b,solutrean_ratiotd_b)

ratio_tooldebitage %>%
  dplyr::mutate(Source = case_when(
    RMTYPE == "TYPE 1" | RMTYPE == "TYPE 2" | RMTYPE == "TYPE 3" | RMTYPE == "TYPE 4" | RMTYPE == "TYPE 5" ~ "Local",
    RMTYPE == "TYPE 6" | RMTYPE == "TYPE 7" | RMTYPE == "TYPE 8" | RMTYPE == "TYPE 9" | RMTYPE == "TYPE 10" | RMTYPE == "TYPE 11" | RMTYPE == "TL" ~ "Non-local")) %>% 
  mutate(RMTYPE = factor(RMTYPE, levels = c("TYPE 1","TYPE 2", "TYPE 3", "TYPE 4",
                                        "TYPE 5", "TYPE 6","TYPE 7", 
                                        "TYPE 8", "TYPE 9", "TYPE 10", "TYPE 11", "TL"))) %>%
  ggplot(aes(x=RMTYPE, y=`Tool/Blank`, shape = Source, colour = Assemblage)) +
  geom_point(size=2)
